Considering scale in multilayer animal social networks

### 2020-06-20 paper/manuscript.Rmd
small edits todo

---
title: Considering scale in multilayer animal social networks
author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: |
  | ^1^Department of Biology, Memorial University of Newfoundland, Canada
  | ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
  | \*Corresponding author: Alec L. Robitaille (robit.alec@gmail.com)
output:
   bookdown::github_document2: default
   # bookdown::word_document2:
   #   reference_docx: template.docx
knit: (function(inputFile, encoding) {
  rmarkdown::render(input = inputFile, encoding = encoding, output_format = "all") })
bibliography: ../references/knitcite.bib
csl: csl.csl
---

@@

# source('../scripts/00-variables.R')

@@

# Introduction
Our inference regarding the processes underlying ecological patterns
are directly linked to the scale at which they are observed [@Levin_1992;
@Allen_2015]. Animals are influenced across scales, through processes such as
species-specific as trophic interactions and resource availability
[@Legendre_1993; @Chave_2013] and global climate and productivity [@Field_2009].
Multiscale ecology has been integrated into species distribution modelling
[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989],
among others. Meanwhile, in the context of animal behaviour, certain behaviours
are scale-dependent; for example, acoustic communication in birds varies with
spatial scales [@Luther_2009]. We posit that it is important to consider that
animal behaviour within the social environment will be scale-dependent.

Sociality exists across both temporal and spatial scales (Whitehead 2008). For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods [e.g. @Carter_2015], whereas social association
represents shared space use by members of the same social group [Figure
\@ref(fig:spacetime), @Franks_2009]. Further, for social interactions or
associations to occur individuals must share space, and thus have overlapping
home ranges [@Vander_Wal_2013]. In the context of the social environment, home
range overlap is an example of how animals share space over coarser spatial and
temporal scales (e.g. Piza-Roca et al. 2018). Although the social environment
clearly scales spatially and temporally, it remains unclear whether coarser
scales of sociality, including social association and home range overlap, vary
predictably with social interaction [@Castles_2014;
@Farine_2015a]. Thus, we define social scale as the type of social relationship
observed that can be explicitly defined and measured [@Farine_2015a].

@@

Unlike traditional monolayer social networks, multilayer networks explicitly
consider social systems across scale-dependent contexts
[@Pilosof_2017]. Multilayer networks are made up of multiple layers, each
representing (i) different classes of individuals, e.g. male or female, (ii)
types of behaviours, e.g. grooming, travelling, or foraging, (iii) spatial
areas, e.g. local or regional, (iv) or temporal windows, e.g. daily or seasonal
[@Kivela_2014; @Porter_2018]. Multilayer networks are relatively novel to
studies of animal behaviour [@Silk_2018; @Finn_2019], although they have been
used to describe multidimensional human social systems, complex transportation
networks, and neural networks [@Silk_2018]. The role of scale within multilayer
social networks remains unexplored but provides a unique opportunity to develop
novel understanding of variation in the social, spatial or temporal scales associated
with social systems.

Our examinations is motivated by behavioural, landscape, and spatial ecology to
build a conceptual and analytical framework for scale-dependent multilayer
networks, and we apply this framework to a case study of caribou (*Rangifer
tarandus*) in Newfoundland, Canada [@Peignier_2019]. We use this case study to
address two principal questions associated with scale-dependent multilayer
networks. First, to what degree does the social scale of relationships, spatial
scale of landscapes, and temporal scale of analysis influence our ability to
interpret complex social systems? Second, can variation in the social, spatial,
and temporal scale improve predictions associated with biological differences in
seasonal resource availability and social association? We conclude with
perspectives for further development and application of scale in multilayer
networks with respect to phenotypes and individual fitness,
movement ecology and collective movement, and habitat selection
and space use.

@@

We generated multilayer networks across a series of spatial distance thresholds
for group assignment. Spatial distance thresholds (5, 25, 50, 75, 100, 250 and
500 m) represented a range of visual (short distance) to auditory (long
distance) sensory modalities of caribou. Multilayer networks consisted of the
social association between `r DT[, uniqueN(get(idcol))]` individuals across
three habitat layers (open, forest and forage) for the entire study period. At
the finest scale, individuals within 5 m of one another were considered in the
same group, whereas at the coarsest scale, individuals within 500 m of one
another were considered in the same group. We calculated graph strength and
multidegree for each habitat layer and spatial distance threshold, and edge
overlap across the entire series of networks to determine proportion of total
edges observed in each combination of habitat layer and spatial distance
threshold.

### Spatial scale
To assess the influence of spatial scale, we aggregated the land cover raster
using the R package `grainchanger` [@Graham_2019] across a series of scales (100
- 1000 m by steps of 100 m). The land cover raster was aggregated using a modal
moving window method using a circular window corresponding to the above scales
[@Graham_2019a]. We assume 30 m and 100 m represents fine-scale decision making
for caribou during foraging, while re-sampling at 500 m , 750 m and 1000 m
represents the scale at which caribou tend to select and avoid habitat
(Bastille-Rousseau et al. 2017). For each spatial scale, we generated a
multilayer network consisting of the social association between 
`r DT[, uniqueN(get(idcol))]` individuals across three habitat layers (open, forest and
forage) for the entire study period. Social associations of individuals were
defined by spatiotemporal overlap within 5 minutes and 50 m. We calculated graph
strength and multidegree for each habitat layer and spatial scale, and edge
overlap across the entire series of networks to determine proportion of total
edges observed in each combination of habitat layer and spatial scale.

### Temporal scale
#### Time windows 
We used a temporal multilayer network to assess the seasonality of caribou
sociality. Multilayer networks consisted of the social association between 
`r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods of 35-36
days taken from the entire study period. Social associations were defined by
spatiotemporal overlap of individuals within 5 minutes and 50 m. In each time
window, we calculated individual graph strength and multidegree, and across the
series of networks, we calculated edge overlap to determine proportion of total
edges observed in each time window.

@@

# Results
Individuals in multilayer networks became more connected as the spatial distance
threshold increased. Mean graph strength differed across habitat layers with
similar and higher graph strength in open and forage layers, and lower strength
in forest layers (Figure \@ref(fig:socres)). Individual graph strength increased
sharply between 5 m and 100 m in all three habitat classes followed by a
decrease in rate after 100 m. These results suggest the optimal social scale at
which groups should be assigned is likely somewhere between ~20 - 100 m based on
the rate at which network metrics stabilized. For ungulates, groups are often
assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018; Peignier
et al. 2019), suggesting that given similar quantities of data, ~50 m is likely
an appropriate social scale for generating social networks in caribou and
similar species.

Increasing land cover resolution resulted in decreased availability of forage,
a rare and patchy habitat, and corresponding low connectivity of individuals in
these habitats at higher resolution (Figure \@ref(fig:lcres)). Graph strength
and edge overlap were relatively consistent across land cover resolutions for
forest and open layers (Figure \@ref(fig:lcres) D, E). Edge overlap decreased
sharply between 30 m and 600 m in forage layers, afterwards remaining stable to
1000 m (Figure \@ref(fig:lcres) D). Graph strength was more variable within
forage layers across land cover resolutions than open and forest (Figure
\@ref(fig:lcres) D). The proportion of relocations in forest and open habitats
increased with increasing spatial resolution, while decreasing in forage habitat
(Supplementary 1 Figure 1).  Overall, these results indicate the importance of
matching land cover resolution to scale of selection as well as ensuring the
land cover product used has a resolution fine enough to detect landscape
features and habitats relevant to study species, such as important patchy and
rare habitats.

The ordinal multilayer network generated indicated within-year time windows of
increased caribou sociality. Edge overlap was higher in time windows 1, 6-11 and
15-20 than in time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A). Time
windows of higher edge overlap, between approximately October and May, had
correspondingly higher graph strength compared to time windows of lower edge
overlap, between approximately May and October (Figure \@ref(fig:temp) C). Graph
strength peaked across the time series in periods 9 and 10. These results
suggest that ordinal multilayer networks can effectively capture discrete time
windows of aggregation and dissaggregation related to resource availability, and
highlight the importance of carefully selecting the temporal scale of analysis.

As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics generally appeared to stabilize.
Graph strength across individuals in all three habitat layers was highly
variable at low number of observations and stabilized after ~100 observations
(Figure \@ref(fig:nobs) A). Edge overlap increased across all three habitat
layers with increasing number of observations (Figure \@ref(fig:nobs) B).
Similarly, multidegree for all individuals increased quickly between 10 and 100
observations, and continued to increase until 1000 observations (Figure
\@ref(fig:nobs) C). Given the observed trend of these multilayer metrics
stabilizing after a certain number of observations are included, the results
suggest this sensitivity method could be useful for determining the number of
observations necessary for sufficiently describing social dynamics across
contexts.

<!-- Figure: metrics by social scale -->
(ref:socres) Varying scale in spatial distance threshold. For each spatial distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open). Graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes. After 100 m, graph strength continued to increase at a slower rate. Open and forage layers showed higher variation in graph strength between individuals while the forest layer had less variation and lower mean graph strength.

<!-- Figure: metrics by land cover resolution -->
(ref:lcres) Varying spatial scale of land cover raster. For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open). A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m). D) Edge overlap of habitat layers across spatial resolutions. Open and forest layers show consistent edge overlap with increasing spatial resolution while forage shows a sharp decline in edge overlap between 30 m and 600 m. Above 600 m, the forage layers are stable. E) Graph strength (mean of individuals in bold) within habitat layers across spatial resolution. Forage layers showed high variation in graph strength with many individuals dropping to 0 after 500 m and others increasing with spatial resolution. Open layers and forest layers were relatively stable across spatial resolutions, with higher mean graph strength in open compared to forest.

<!-- Figure: metrics by number of observations -->
(ref:nobs) Varying scale in number of observations. Multilayer networks were generated using a  sample number of observations (10 - 1000 observations by steps of 10) of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open). A) Graph strength was highly variable at low number of observations (less than 100) for all habitat layers and relatively stable after 200 observations. B) Edge overlap increased for all habitat layers with increasing number of observations. Open and forage layers had higher edge overlap than forest layers. C) Multidegree increased for all individuals with increasing number of observations. Individuals showed high variability (`r nobs[nobs == max(nobs), paste(range(multideg), collapse = ' - ')]`) at the maximal number of observations (1000).

<!-- Figure: Time window -->
(ref:temp) Varying temporal scale in multilayer networks. Multilayer networks were generated of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within ordinal time windows (20 ordinal sample periods of 35-36 days) between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`. A) Edge overlap across time windows showed two periods of low overlap (time windows 2-5 and 12-15), and three periods of high overlap (time windows 1, 6-11, 15-20). B) Ordinal network layers showing unweighted edges between individuals within time windows. Like edge overlap, individuals were more connected in time windows 1, 6-11, and 15-20, compared to 2-5 and 12-15. C) Graph strength within time windows showing individuals as thin grey lines and mean across individuals as thick grey lines. Graph strength peaked in time window 9, with noticeable higher strength than the following year.

@@

Our results highlight the influence of social, spatial and temporal scale on
multilayer networks. For social scale, we found individuals became more
connected with increasing spatial distance threshold. Increasing land cover
resolution lead to a decrease in availability of patchy and rare habitats and,
correspondingly, lower connectivity of individuals in these habitats. Temporal
windows highlighted clear periods of increased sociality among individuals.
Finally, increasing number of observations lead to a general stabilizing in network
metrics. As such, scale is inherently tied to the generation  of multilayer
networks and metrics evaluating them, as well as the individual layers that make
them up.

Monolayer network approaches have been increasingly used to link social network
position with individual fitness, including in primates [@Brent_2017;
@Thompson_2019], dolphins [@Stanton_2012; @Stanton_2011], and birds
[@McDonald_2007; @Royle_2012]. Social scale has emerged as an important variable
for understanding fitness consequences in the context of social network
positions <!-- TODO JWT check --> [@Almeling_2016; @Berger_2015; @Brent_2017;
@Holekamp_2011]. Defining the social scale at which to generate networks is an
essential consideration for social network analysis <!-- with direct impacts on
outcomes blah-->[@Castles_2014; @Carter_2015; @Farine_2015a]. Proximity-based
social networks generated using GPS location data require using a social scale,
specifically a spatial distance threshold, to define social associations. We
found increasing individual graph strength across three habitat layers with
increasing spatial distance threshold (Figure \@ref(fig:socres)). In addition,
habitat layers differed in their response to spatial distance threshold, with
open and forage with a larger increase in graph strength and greater variation
across individuals. These results emphasize that multilayer network metrics are
directly influenced by social scale, in this case the spatial distance
threshold.

@@

The emergent relationship between habitat and sociality has been explored by the
distribution and phenology of resources and use of social information. For
example, cougar (*Puma concolor*) home ranges overlapped more in regions with
high hunting opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou
(*Rangifer tarandus*) sociality differed between seasons, where social
associations were stronger in winter and contrastingly low in summer when
resource availability are more homogeneous [@Peignier_2019]. Bison (*Bison
bison*) showed stronger habitat selection in larger groups and avoidance of
predation risk was a main factor contributing to their habitat selection
[@Fortin_2009]. These examples, comparing sociality and habitat selection across
temporal or spatial contexts, are implicitly multilayer analyses.

Multilayer networks represent a novel framework for explicitly testing the
influence of habitat selection on sociality across scales. Animal social systems
can be parsed by spatial contexts, for example as defined by habitat types as in
Figure \@ref(fig:lcres). Given that habitat data are available across a wide
range of spatial scales, we evaluated the influence of habitat spatial
resolution on multilayer network metrics. The results indicate varied influence
of increasing spatial resolution depending on the habitat layer. As spatial
resolution increased, edge overlap decreased in forage while remaining stable in
open and forest habitats (Figure \@ref(fig:socres) D). Forage is a rare and
patchy habitat on Fogo Island, as is indicated by a decrease in the proportion
of relocations in this habitat type with increasing spatial resolution (Supplementary 1
Figure 1). Similar to increasing spatial distance threshold, the influence
of increasing spatial resolution on graph strength was notably different between
habitat layers. Forest layers showed little change in graph strength with
increasing spatial resolution and variation between individuals. Forage and open
layers had greater individual variation in graph strength, while forage was the
sole layer to show large responses in graph strength to increasing spatial
resolution (Figure \@ref(fig:socres) E). As such, multilayer network measures
related to habitat are explicitly dependent on spatial scale. Edge overlap can
indicate if some associations between individuals are dependent on the
habitat-context [@Battiston_2014]. If the spatial resolution of the habitat data
are insufficient to capture rare habitats, context-specific relationships
between individuals may not be captured by multilayer networks.

>>>>

---
title: Considering scale in multilayer animal social networks
author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: |
  | ^1^Department of Biology, Memorial University of Newfoundland, Canada
  | ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
  | \*Corresponding author: Alec L. Robitaille (robit.alec@gmail.com)
output:
   # bookdown::github_document2: default
   bookdown::word_document2:
     reference_docx: template.docx
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding,
  output_format = "all") })
bibliography: ../references/knitcite.bib
csl: csl.csl
---

@@

source('../scripts/00-variables.R')

@@

# Introduction
Our inference regarding the processes underlying ecological patterns
are directly linked to the scale at which they are observed [@Levin_1992;
@Allen_2015]. Animals are influenced across scales, through ecological processes such as
species-specific trophic interactions, resource availability
[@Legendre_1993; @Chave_2013], and global climate and productivity [@Field_2009].
<!-- JWT: I'm not sure exactly what that sentence was trying to say so my edits may not work -->
Multiscale ecology has been integrated into species distribution modelling
[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989],
among other processes. Meanwhile, in the context of animal behaviour, certain behaviours
are scale-dependent; for example, acoustic communication in birds varies with
spatial scales [@Luther_2009]. We posit that it is important to consider that
animal behaviour within the social environment will be scale-dependent. 
<!-- QW: I think this last sentence needs to be a bit stronger. Why is it important? -->

Sociality exists across both temporal and spatial scales (Whitehead 2008). For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods [e.g. @Carter_2015], whereas social association
represents shared space use by members of the same social group [Figure
\@ref(fig:spacetime), @Franks_2009]. Further, for social interactions or
associations to occur individuals must share space, and thus have overlapping
home ranges [@Vander_Wal_2013]. In the context of the social environment, home
range overlap is an example of how animals share space over coarser spatial and
temporal scales (e.g. Piza-Roca et al. 2018). Although the social environment
clearly scales spatially and temporally, it remains unclear whether coarser
scales of sociality, including social association and home range overlap, vary
predictably with social interaction [@Castles_2014;
@Farine_2015a]. We therefore define social scale as the type of social relationship
observed that can be explicitly defined and measured [@Farine_2015a] and suggest the 
potential for adaptive variance in social relationships is also scale-dependent. 
<!--QW: also need to fix up this last sentence- I added the 'adaptive variance part 
under the expectation that there is some scale at which variance is greatest, and presumably
it is this scale that has the greatest effect on fitness or other traits-->

@@

Unlike traditional monolayer social networks, multilayer networks explicitly
consider social systems across scale-dependent contexts
[@Pilosof_2017]. Multilayer networks are made up of multiple layers, each
representing (i) different classes of individuals, e.g. male or female, (ii)
types of behaviours, e.g. grooming, travelling, or foraging, (iii) spatial
areas, e.g. local or regional, (iv) or temporal windows, e.g. daily or seasonal
[@Kivela_2014; @Porter_2018]. Multilayer networks are relatively novel to
studies of animal behaviour [@Silk_2018; @Finn_2019], although they have been
used to describe multidimensional human social systems, complex transportation
networks, and neural networks [@Silk_2018]. <!-- just "scale".. edit sent -->The role of scale within multilayer
social networks remains unexplored but provides a unique opportunity to develop
novel understanding of variation in the social, spatial, or temporal scales associated
with social systems.

<!-- we examined-->Our examinations are motivated by behavioural, landscape, and spatial ecology to
build a conceptual and analytical framework for scale-dependent multilayer
networks, and we apply this framework to a case study of caribou (*Rangifer
tarandus*) in Newfoundland, Canada [@Peignier_2019]. We use this case study to
address two principal questions associated with scale-dependent multilayer
networks. First, to what degree does the social scale of relationships, spatial
scale of landscapes, and temporal scale of analysis influence our ability to
interpret complex social systems? Second, can variation in the social, spatial,
and temporal scale improve <!-- replace pred-->predictions associated with biological differences in
seasonal resource availability and social association? We conclude with
perspectives for further development and application of scale in multilayer
networks with respect to phenotypes and individual fitness,
movement ecology and collective movement, and habitat selection
and space use.
<!-- JWT: This part may have to change depending on how we do the disc -->

@@

We generated multilayer networks across a series of spatial distance thresholds 
that relate to behavioural interactions that could occur within those distances
<!-- JWT: or something like that needs to be in the first sentence to relate the spatial distance to social scale upfront -->
for group assignment. Spatial distance thresholds (5, 25, 50, 75, 100, 250 and
500 m) represented a range of visual (short distance) to auditory (long
distance) sensory modalities of caribou. Multilayer networks consisted of the
social association between `r DT[, uniqueN(get(idcol))]` individuals across
three habitat layers (open, forest and forage) for the entire study period. At
the finest scale, individuals within 5 m of one another were considered in the
same group, whereas at the coarsest scale, individuals within 500 m of one
another were considered in the same group. We calculated graph strength and
multidegree for each habitat layer and spatial distance threshold, and edge
<!-- JWT: can we call spatial distance social distance? -->
overlap across the entire series of networks to determine proportion of total
edges observed in each combination of habitat layer and spatial distance
threshold.

### Spatial scale
To assess the influence of spatial scale, we aggregated the land cover raster
using the R package `grainchanger` [@Graham_2019] across a series of scales (100
- 1000 m by steps of 100 m). The land cover raster was aggregated using a modal
moving window method using a circular window corresponding to the above scales
[@Graham_2019a]. We assume 30 m and 100 m represents fine-scale decision making
for caribou during foraging, while re-sampling at 500 m , 750 m and 1000 m
represents the scale at which caribou tend to select and avoid habitat
(Bastille-Rousseau et al. 2017). For each spatial scale, we generated a
multilayer network consisting of the social associations between 
`r DT[, uniqueN(get(idcol))]` individuals across three habitat layers (open, forest and
forage) for the entire study period. Social associations of individuals were
defined by spatiotemporal overlap within 5 minutes and 50 m. We calculated graph
strength and multidegree for each habitat layer and spatial scale, and edge
overlap across the entire series of networks to determine proportion of total
edges observed in each combination of habitat layer and spatial scale.
<!-- JWT: Your graphs present things in the order of Forage, Forest, Open, but in the text you do open, forest, forage. They need to be consistent -->

### Temporal scale
#### Time windows 
We used a temporal multilayer network to assess the seasonality of caribou
sociality. Multilayer networks consisted of the social associations between 
`r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods of 35-36 <!--QW: why 35-36 and not just 35 or 36?-->
days taken from the entire study period. Social associations were defined by
spatiotemporal overlap of individuals within 5 minutes and 50 m. In each time
window, we calculated individual graph strength and multidegree, and across the
series of networks, we calculated edge overlap to determine proportion of total
edges observed in each time window.

@@

# Results
Individuals in multilayer networks became more connected as the spatial distance
<!-- JWT: I really think calling it spatial distance is misleading given we want to represent social scale. Even if we stick with calling it spatial distance (I see you call it social distance in the graph), we need to lead in calling it social scale so the reader knows that's what we're referencing. -->
threshold increased. Mean graph strength differed across habitat layers with
similar and higher graph strength in open and forage layers, and lower strength
in forest layers (Figure \@ref(fig:socres)). Individual graph strength increased
sharply between 5 m and 100 m in all three habitat classes followed by a plateau in
the rate of increase after 100 m (<!--TODO: figure XX-->). 
These results suggest the optimal social scale at
which groups should be assigned is between ~20 - 100 m based on
the rate at which network metrics <!--QW: which metrics?--> stabilized. For ungulates, groups are often
assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018; Peignier
et al. 2019), suggesting that given similar quantities of data, ~50 m is likely
an appropriate social scale for generating social networks in caribou and
similar species. <!--QW: I'm not sure about this statement. Should it be more about 
how GPS data allows (e.g. from this study and Peignier et al; Lesmerises et al.) us to confirm 
the use of 50m buffer that has long been used for studies in the field (e.g. Lingle 2003 and 
any Clutton-Brock red deer paper that uses group size data)-->

Increasing land cover resolution resulted in decreased availability of foraging habitat 
<!--QW: I think we need to call this foraging habitat, when possible... forage to me 
refers to the thing an animal is eating-->,
a rare and patchy habitat, and corresponding low connectivity of individuals in
these habitats at higher resolution (Figure \@ref(fig:lcres)). Graph strength
and edge overlap were relatively consistent across land cover resolutions for
forest and open layers (Figure \@ref(fig:lcres) D, E). Edge overlap decreased
sharply between 30 m and 600 m in forage layers, afterwards remaining stable to
1000 m (Figure \@ref(fig:lcres) D). Graph strength was more variable within
foraging habitat layers across land cover resolutions than open and forest habitat layers (Figure
\@ref(fig:lcres) D). <!-- JWT: the order things are discussed here is a little confusing, you discuss strength, edge overlap, then strenght again. I think this should be reordered so it's easier to follow. -->
The proportion of relocations in forest and open habitats
increased with increasing spatial resolution, while decreasing in foraging habitat
(Supplementary 1 Figure 1).  Overall, these results indicate the importance of
matching land cover resolution to scale of selection as well as ensuring the
land cover product used has a resolution fine enough to detect landscape
features and habitats relevant to study species, such as important patchy and
rare habitats.

<!--QW: what makes it ordinal again? Is it ordinal OR continuous? -->
The ordinal multilayer network generated indicated within-year time windows of
increased caribou sociality. <!--QW: I'm not sure what you are trying to say in this first sentence. Is it that there are distinct within-year time windows where social network metrics increased? -->
Edge overlap was higher in time windows 1, 6-11 and
15-20 than in time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A). <!--QW: I'm not sure about using the window number - it doesn't really mean anyhting. Can you use actual dates?--> Time
windows of higher edge overlap, between approximately October and May, had
correspondingly higher graph strength compared to time windows of lower edge
overlap, between approximately May and October (Figure \@ref(fig:temp) C). Graph
strength peaked across the time series in periods 9 and 10. These results
suggest that ordinal multilayer networks can effectively capture discrete time
windows of aggregation and dissaggregation related to resource availability, and
highlight the importance of carefully selecting the temporal scale of analysis.

As one might expect, when the number of observations used to generate multilayer networks increased,
individuals became more connected and variance in metrics decreased. <!--QW: I think throughout you want to say "variance decreased" instead of "stabilized" -->
Graph strength across individuals in all three habitat layers was highly
variable at low number of observations and stabilized after ~100 observations
(Figure \@ref(fig:nobs) A). Edge overlap increased across all three habitat
layers with increasing number of observations (Figure \@ref(fig:nobs) B).
Similarly, multidegree for all individuals increased quickly between 10 and 100
observations, and continued to increase until 1000 observations (Figure
\@ref(fig:nobs) C). Given the observed trend of these multilayer metrics
stabilizing after a certain number of observations are included, the results
suggest this sensitivity method could be useful for determining the number of
observations necessary for sufficiently describing social dynamics across
contexts.

<!-- Figure: metrics by social scale -->
(ref:socres) Varying scale in social distance threshold. For each social distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (*R. tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open). Graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes. After 100 m, graph strength continued to increase at a slower rate. Open and forage layers showed higher variation in graph strength between individuals while the forest layer had less variation and lower mean graph strength.

<!-- Figure: metrics by land cover resolution -->
(ref:lcres) Varying spatial scale of land cover raster. For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (*R. tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open). A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m). D) Edge overlap of habitat layers across spatial resolutions. Open and forest layers show consistent edge overlap with increasing spatial resolution while forage shows a sharp decline in edge overlap between 30 m and 600 m. Above 600 m, the forage layers are stable. E) Graph strength (mean of individuals in bold) within habitat layers across spatial resolution. Forage layers showed high variation in graph strength with many individuals dropping to 0 after 500 m and others increasing with spatial resolution. Open layers and forest layers were relatively stable across spatial resolutions, with higher mean graph strength in open compared to forest.

<!-- Figure: metrics by number of observations -->
(ref:nobs) Varying scale in number of observations. Multilayer networks were generated using a  sample number of observations (10 - 1000 observations by steps of 10) of caribou social associations (*R. tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open). A) Graph strength was highly variable at low number of observations (less than 100) for all habitat layers and relatively stable after 200 observations. B) Edge overlap increased for all habitat layers with increasing number of observations. Open and forage layers had higher edge overlap than forest layers. C) Multidegree increased for all individuals with increasing number of observations. Individuals showed high variability (`r nobs[nobs == max(nobs), paste(range(multideg), collapse = ' - ')]`) at the maximal number of observations (1000).

<!-- Figure: Time window -->
(ref:temp) Varying temporal scale in multilayer networks. Multilayer networks were generated of caribou social associations (*R. tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within ordinal time windows (20 ordinal sample periods of 35-36 days) between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`. A) Edge overlap across time windows showed two periods of low overlap (time windows 2-5 and 12-15), and three periods of high overlap (time windows 1, 6-11, 15-20). B) Ordinal network layers showing unweighted edges between individuals within time windows. Like edge overlap, individuals were more connected in time windows 1, 6-11, and 15-20, compared to 2-5 and 12-15. C) Graph strength within time windows showing individuals as thin grey lines and mean across individuals as thick grey lines. Graph strength peaked in time window 9, with noticeable higher strength than the following year.

<!-- JWT: edge overlap, graph strength, and multidegree are presented in different orders in the graphs. They should be presented in the same order each time even if the combination of what you show changes. -->

@@

Our results highlight the influence of social, spatial and temporal scale on
multilayer networks. For social scale, we found individuals became more
connected with increasing spatial distance threshold. Increasing land cover
resolution lead to a decrease in availability of patchy and rare habitats and, 
<!--QW: not sure I'd mention 'rare' since there are only 3 habitat types. 
Could you just say 'less common' or even just 'patchy'?-->
correspondingly, lower connectivity of individuals in these habitats. Temporal
windows highlighted clear periods of increased sociality among individuals.
Finally, increasing number of observations led to a general stabilization in network
metrics. As such, scale is inherently tied to the generation  of multilayer
networks and metrics evaluating them, as well as the individual layers that make
them up.
<!--QW: I will pre-empt Eric and say I think this paragraph could maybe not mention the results at all. 
You could focus on just talking about the importance of scale for behavioural and spatial ecology.
Why is it important and what are the more broadly applicable ideas that lead us to this paper? 
Maybe keep this little summary paragraph for now - I think likely we could integrate what I describe 
above with what you already have-->

Monolayer network approaches have been increasingly used to link social network
position with individual fitness, including in primates [@Brent_2017;
@Thompson_2019], dolphins [@Stanton_2012; @Stanton_2011], and birds
[@McDonald_2007; @Royle_2012]. Social scale has emerged as an important variable
for understanding fitness consequences in the context of social network
positions <!-- TODO JWT check-- JWT: these are right, and we could potentially replace the holekamp paper with our recent JAE one if it gets released in time --> [@Almeling_2016; @Berger_2015; @Brent_2017;
@Holekamp_2011]. Defining the social scale to generate networks is an
essential consideration for social network analysis <!-- with direct impacts on
outcomes blah-->[@Castles_2014; @Carter_2015; @Farine_2015a]. Proximity-based
social networks generated using GPS location data require using a social scale,
specifically a spatial distance threshold, to define social associations. We
found increasing individual graph strength across three habitat types with
increasing spatial distance threshold (Figure \@ref(fig:socres)). <!-- This means blah blah for different types of interactions.--> In addition, 
habitat layers differed in their response to spatial distance threshold, with
open and forage with a larger increase in graph strength and greater variation
across individuals. <!-- What could this mean biologically? --> These results emphasize that multilayer network metrics are
directly influenced by social scale, in this case the spatial distance
threshold.

@@

The emergent relationship between habitat and sociality has been explored by the
distribution and phenology of resources and use of social information. For
example, cougar (*Puma concolor*) home ranges overlapped more in regions with
high hunting opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou
(*R. tarandus*) social network graph strength differed between seasons, where 
graph strength was stronger in winter and contrastingly low in summer when
resource availability are more homogeneous [@Peignier_2019]. Bison (*Bison
bison*) showed stronger habitat selection in larger groups, and avoidance of
predation risk was a main factor contributing to their habitat selection
[@Fortin_2009]. These examples, comparing sociality and habitat selection across
temporal or spatial contexts, are implicitly multilayer analyses.

Multilayer networks represent a novel framework for explicitly testing the
influence of habitat selection on sociality across scales. Animal social systems
can be parsed by spatial contexts, for example as defined by habitat types as in
Figure \@ref(fig:lcres). Given that habitat data are available across a wide
range of spatial scales, we evaluated the influence of habitat spatial
resolution on multilayer network metrics. The results indicate varied influence
of increasing spatial resolution depending on the habitat layer. As spatial
resolution increased, edge overlap decreased in forage while remaining stable in
open and forest habitats (Figure \@ref(fig:socres) D). Forage <!--Lichen? I think we need to call this lichen and not forage --> is a rare (<!--TODO--> XX % of the landscape) and
patchy habitat on Fogo Island, as is indicated by a decrease in the proportion
of relocations in this habitat type with increasing spatial resolution (Supplementary 1
Figure 1). Similar to increasing social distance threshold, the influence
of increasing spatial resolution on graph strength was notably different between
habitat layers. Forest layers showed little change in graph strength with
increasing spatial resolution and variation between individuals. Lichen and open
layers had greater individual variation in graph strength, while lichen was the
only layer to show large responses in graph strength to increasing spatial
resolution (Figure \@ref(fig:socres) E). As such, multilayer network measures
related to habitat are explicitly dependent on spatial scale. Edge overlap can
indicate if some associations between individuals are dependent on the
habitat-context [@Battiston_2014]. If the spatial resolution of the habitat data
are insufficient to capture rare habitats, context-specific relationships
between individuals may not be captured by multilayer networks.
